---
title: "Final presentation : Creating a Shiny Application to find an appartment in Lausanne "
author: "Arnaud Bertrand, Meriem Ben Mustapha, Alexandre Gautschi, Lawrence Jesudasan,
  Fabien Calderini"
date: "`r Sys.Date()`"
output: 
  ioslides_presentation:
    font_adjustment: 1
    widescreen: yes
  beamer_presentation: default
---

```{css, echo = FALSE}
.remark-slide-content {
  font-size: 28px;
  padding: 20px 80px 20px 80px;
}
.remark-code, .remark-inline-code {
  background: #f0f0f0;
}
.remark-code {
  font-size: 24px;
}
.huge .remark-code { /*Change made here*/
  font-size: 200% !important;
}
.tiny .remark-code { /*Change made here*/
  font-size: 50% !important;
}
```

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r, echo=FALSE, warning=FALSE, message=FALSE}
library(tidyverse)
library(tidytext)
library(quanteda)
library(quanteda.textmodels)
library(quanteda.textstats)
library(quanteda.textplots)
library(textdata)
```


# Introduction and Objectives

## Objectives and potential impacts

- Understand the value addition of Text Mining
- Being able to carry our Exploratory Data Analysis (EDA) on text data using R
- Apply unsupervised methods for topic modeling
- Develop several supervised models using text
- Practice and master the tidy text and `quanteda` packages in R

## Project description  

* Methods used 
* What inspired us ? 
* How did we collect the data ? What are the risks of using this strategy ? 


# Webscrapping  

## Immoscout website


# R Package creation   

## Package functions 


# Shiny App

## Price estimation 

## Find the 5 most similar appartments 

## Impact of square meters on the price 

